TGI-spine

### 2022-04-07 analysis/tgispine_hypotheses.Rmd
adding pilot data to shape hypotheses, and correcting labelling error

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:35,1), sd=10)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(10:40,1), sd=10)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(10:45,1), sd=10)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:50,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:65,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:50,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=5)

# Burning ratigs: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:80,1), sd=15)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:65,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:50,1), sd=15)
# 
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(5:25,1), sd=5)

@@

col_cold_n <- blues[5]
col_cold_w <- blues[3]
col_warm_n <- reds[3]
col_warm_w <- reds[5]
col_unpl_n <- purps[3]
col_unpl_w <- purps[5]

@@

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(blues[6],blues[3])) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c(blues[6], "gray25")) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Cold ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 1: Cold perception')

@@

```{r, echo=FALSE}
# Subset of data corresponding to cold ratings
df_subj_warm  <- subset(df_subj, quality == "warm")
df_group_warm <- subset(df_group, quality == "warm")

@@

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "caudal", "rostral"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_warm_n, col_warm_w)) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", reds[6])) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Warm ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 1: Warm perception')

w1
```

>>>>

# The following intervals and mean can be changed to reflect hypotheses
# Cold ratigs: simulation
w_dr_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_tgi_cold <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_tgi_cold <- rnorm(trialN, mean=sample(5:45,1), sd=15)
a_pc_tgi_cold <- rnorm(trialN, mean=sample(5:40,1), sd=15)
w_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
w_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_dr_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)
a_pc_nontgi_cold <- rnorm(trialN, mean=sample(10:55,1), sd=15)

# Warm ratigs: simulation
w_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
w_pc_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=10)
a_dr_tgi_warm <- rnorm(trialN, mean=sample(10:80,1), sd=15)
a_pc_tgi_warm <- rnorm(trialN, mean=sample(5:60,1), sd=15)
w_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
w_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_dr_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)
a_pc_nontgi_warm <- rnorm(trialN, mean=sample(5:25,1), sd=10)

# Burning ratings: simulation
 w_dr_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 w_pc_tgi_burn <- rnorm(trialN, mean=sample(10:50,1), sd=10)
 a_dr_tgi_burn <- rnorm(trialN, mean=sample(10:40,1), sd=15)
 a_pc_tgi_burn <- rnorm(trialN, mean=sample(5:30,1), sd=15)
# 
 w_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 w_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_dr_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)
 a_pc_nontgi_burn <- rnorm(trialN, mean=sample(0:10,1), sd=5)

@@

col_cold_n <- blues[5]
col_cold_w <- blues[3]
col_warm_n <- reds[3]
col_warm_w <- reds[5]
col_burn_n <- purps[3]
col_burn_w <- purps[5]

@@

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(blues[6],blues[3])) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c(blues[6], "gray25")) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Cold ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 1: Cold perception')

@@

```{r, echo=FALSE}
# Subset of data corresponding to warm ratings
df_subj_warm  <- subset(df_subj, quality == "warm")
df_group_warm <- subset(df_group, quality == "warm")

@@

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_warm_n, col_warm_w)) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", reds[6])) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Warm ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 2: Warm perception')

w1
```
## Plot burn ratings

```{r, echo=FALSE}
# Subset of data corresponding to warm ratings
df_subj_burn  <- subset(df_subj, quality == "burn")
df_group_burn <- subset(df_group, quality == "burn")

# Set jitter for geom_point
set.seed(321)
df_subj_burn$xj <- jitter(df_subj_burn$conditionN, amount=.1)

b1 <- ggplot(data = df_subj_burn, mapping = aes(x = conditionN, y = x, fill = stimuli, shape = stimuli, color = stimuli)) +

   # Add half violin plots
   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
   tgi_half_violin(df_subj_burn, "within", "prox_caud", "non-tgi", nudge2, col_burn_n) +
   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "non-tgi", nudge2, col_burn_n) +
   tgi_half_violin(df_subj_burn, "across", "prox_caud", "non-tgi", nudge2, col_burn_n) +
   tgi_half_violin(df_subj_burn, "within", "dist_rostr", "tgi", nudge1, col_burn_w) +
   tgi_half_violin(df_subj_burn, "within", "prox_caud", "tgi", nudge1, col_burn_w) +
   tgi_half_violin(df_subj_burn, "across", "dist_rostr", "tgi", nudge1, col_burn_w) +
   tgi_half_violin(df_subj_burn, "across", "prox_caud", "tgi", nudge1, col_burn_w) +

   # Add group summary stats (between-condition lines, errors bars, and means)
   geom_line(data = df_group_burn %>% filter(stimuli == "non-tgi"), aes(x = conditionN + .45, y = mean)) +
   geom_line(data = df_group_burn %>% filter(stimuli == "tgi"), aes(x = conditionN + .35, y = mean)) +

   tgi_group_error(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
   tgi_group_error(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n) +
   tgi_group_error(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n) +
   tgi_group_error(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n) +
   tgi_group_error(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w) +
   tgi_group_error(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w) +
   tgi_group_error(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w) +
   tgi_group_error(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w) +

   tgi_group_mean(df_group_burn, "within", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
   tgi_group_mean(df_group_burn, "within", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
   tgi_group_mean(df_group_burn, "across", "dist_rostr", "non-tgi", nudge3, col_burn_n, 22) +
   tgi_group_mean(df_group_burn, "across", "prox_caud", "non-tgi", nudge3, col_burn_n, 22) +
   tgi_group_mean(df_group_burn, "within", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
   tgi_group_mean(df_group_burn, "within", "prox_caud", "tgi", nudge2, col_burn_w, 21) +
   tgi_group_mean(df_group_burn, "across", "dist_rostr", "tgi", nudge2, col_burn_w, 21) +
   tgi_group_mean(df_group_burn, "across", "prox_caud", "tgi", nudge2, col_burn_w, 21) +

   # Define additional settings
   scale_shape_manual(values = c(22, 21)) +
   scale_x_continuous(breaks=c(1.2, 2.2, 3.2, 4.2), labels=c("distal", "proximal", "rostral", "caudal"), limits=c(0.6, 5)) +
   scale_fill_manual(labels = c("non-TGI", "TGI"), values=c(col_burn_n, col_burn_w)) +
   scale_color_manual(labels = c("non-TGI", "TGI"), values=c("gray25", purps[6])) +
   guides(shape = FALSE) +
   labs(title = "", x = "", y = "Burn ratings", fill = "Stimuli", color = "Stimuli") +
   ggtitle('Figure 3: Burn perception')

b1
```
